%====================
% PROJECT A
%====================
\subsection{{\href{https://github.com/mrsamirr/payment-application}{Payment Application} \hfill May 2024}}
\begin{zitemize}
\item {\textbf{This project is a payment application built using MERN stack. It offers simple and effective way to manage payments -}}
\item {\textbf{User Authentication}} : Secure login and registration using {\textbf{JWT (JSON Web Tokens)}}.
\item {\textbf{Payment Gateway Integration}} : Seamless integration with payment gateways to handle transactions.
\item {\textbf{Dashboard}}: Personalized user dashboard to view and manage transactions.
\item {\textbf{Admin Panel}}: Administrative interface to oversee and manage user transactions.
\item {\textbf{Responsive Design}}: Fully responsive design for an optimal user experience on both desktop and mobile devices.
\item {\textbf{RESTful API}}: Well-structured RESTful API for managing all backend operations.

\end{zitemize}

%====================
% PROJECT B
%====================

\subsection{{\href{https://github.com/mrsamirr/todo-app}{TODO - App} \hfill Apr 2024 }}
\begin{zitemize}
\item {\textbf{User Authentication}} : Secure login and registration system.
\item {\textbf{Task Management}} : Create, read, update, and delete tasks.
\item {\textbf{Task Categorization}}: Organize tasks into categories for better management.


\end{zitemize}

% %====================
% % PROJECT C
% %====================
% \subsection{{\href{https://www.agautomobile.com}{AG Automobile} \hfill July 2022}}
% \begin{zitemize}
% \item Created a content-driven website for AG Automobile, using \textbf{Next.js} and \textbf{Tailwind CSS} for seamless user experience and optimized performance, integrated with \textbf{Strapi} CMS for efficient content management.
% \item Deployed the website on \textbf{Vercel} for fast global delivery and automatic scaling.
% \end{zitemize}